### 2014-10-30 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL ECS: add figure, update report

\chapter{Emissions Control System}
\label{ecs}
The emissions control system for the NFRL is a combination spray dryer and pulse jet fabric filter system. The purpose is to remove both particulates and polluntants produced from experiments within the laboratory. Fans draw air through one of four fire calorimter exhaust hoods designed to capture combustion gases from experiments (see Table~\ref{tab:hoods}). Makeup air is drawn into the building via air intake dampers, to replace the air pulled through the exhaust hoods and into the process ducting. Before entering the spray dryer, the air passes through an inline duct burner. The purpose of the duct burner is to heat the air to 500~$^{\circ}$C to improve the efficiency of the spray dryer. Downstreat of the burner, the hot exit air helps to evaporate the limey slury mist generated by the spray dryer. The gas-phase lime reacts with airborne poluntants to form precipitate which collects at the bottom of the dryer, out of the air stream. The spray dryer also introduces a cool water mist to drop the exit temperature of the air below the threshold temperature for the final component, the baghouse. Air enters the baghouse and flows through a series of filter bags. A filter bag is constructed of a long cylindrical metal cage covered with a fine pore fabric. Contaiminated air flows from the outside of the cylinder through the porous media, which traps the particulates, and allows the clean air to flow out through the center of the cylinder.

@@

>>>>

\chapter{Emissions Control System (ECS)}
\label{ecs}
The emissions control system for the NFRL is a combination spray dryer and pulse jet fabric filter system. The purpose is to remove both particulates and polluntants produced from experiments within the laboratory. Fans draw air through one of four fire calorimter exhaust hoods designed to capture combustion gases from experiments (see Table~\ref{tab:hoods}). Makeup air is drawn into the building via air intake dampers, to replace the air pulled through the exhaust hoods and into the process ducting. Before entering the spray dryer, the air passes through an inline duct burner. The purpose of the duct burner is to heat the air to 500~$^{\circ}$C to improve the efficiency of the spray dryer. Downstreat of the burner, the hot exit air helps to evaporate the limey slury mist generated by the spray dryer. The gas-phase lime reacts with airborne poluntants to form precipitate which collects at the bottom of the dryer, out of the air stream. The spray dryer also introduces a cool water mist to drop the exit temperature of the air below the threshold temperature for the final component, the baghouse. Air enters the baghouse and flows through a series of filter bags. A filter bag is constructed of a long cylindrical metal cage covered with a fine pore fabric. Contaiminated air flows from the outside of the cylinder through the porous media, which traps the particulates, and allows the clean air to flow out through the center of the cylinder. Finally the cleaned air exits the system through a 30.5~m exhaust stack which pulls the airflow out using an induction fan.

The complete ECS consists of 4 duct burners, spray dryers, and bag houses, which in pairs of two, exhaust through one of two exhaust stacks. The system is capable of handling a maximum exhaust air flow rate of 5100~m$^3$/min ($\approx$ 20~MW fire), cleaning 5.4 kg/hr of acid gas (HCl) and trapping 181 kg/hr of particulates. Figure~\ref{fig:NFRL_roof} is an aeral photograph of the NFRL which highlights the location of the components of the ECS. Note that components labeled 1 and 2 were part of the inital system while components 3 and 4 were added with the expansion of the laboratory.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\textwidth]{../Figures/nfrl_roof}
\caption {Aeral view of the NFRL with callouts indicating components of ECS.}
\label{fig:NFRL_roof}
\end{figure}
